---
title: "`r desc::desc_get('Title', '..')`"
author: "Hao Ye"
institute: "Health Science Center Libraries"
date: "(updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    seal: false
    fig_caption: false
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_solarized_light(
  base_font_size = "32px", 
  header_h1_font_size = "2.0rem",
  header_h2_font_size = "1.5rem",
  header_h3_font_size = "1.25rem", 
  header_background_content_padding_top = "2rem", 
  header_font_google = google_font("Lato"),
  text_font_google   = google_font("Montserrat", "300", "300i", "500"),
  code_font_google   = google_font("Source Code Pro", "300", "500"), 
  extra_css = list("p" = list("margin-block-start" = "0.5em", 
                              "margin-block-end" = "0.5em"), 
                   "ul" = list("margin-block-start" = "0.5em", 
                              "margin-block-end" = "0.5em"), 
                   "li" = list("margin-block-start" = "0.5em", 
                              "margin-block-end" = "0.5em"), 
                   "pre" = list("margin-top" = "0.5em", 
                              "margin-bottom" = "0.5em"), 
                   ".small" = list("font-size" = "80%"), 
                   ".tiny" = list("font-size" = "50%")),  
  link_color = "#339944"
)
```
class: inverse, center, middle

# `r desc::desc_get('Title', '..')`
### `r rmarkdown::metadata$author`
### `r rmarkdown::metadata$institute`
### (updated: `r Sys.Date()`)

---
You have a published data analysis.

--

### .center[🎉 Congrats! 🎉]

--

What happens next?

--

* Can **I** apply the code to **new** data?
* Can **I** apply **my method** to your data?
* **Where** do you store older versions / figures that didn't make it into the paper?
* How does someone contribute to the project?

---
# Preliminaties

This lesson assumes you:
`r gsub("\n ", "\n", desc::desc_get("prerequisites"))`

--

**NO** previous experience with Git or GitHub is required!

---
# Learning Objectives

1 hour is insufficient to teach you how to use Git and GitHub in a data analysis workflow.

--

1 hour **is** sufficient to explain why Git and GitHub are useful in a data analysis workflow.

---
This lesson teaches you to:

`r gsub("\n ", "\n", desc::desc_get("learningOutcomes"))`

---

class: inverse, center, middle

# Basic Concepts

---

# Version Control

**Version Control**: tools/systems to manage changes to files

--
## You are probably already using version control!

* MS Word has "track changes"
* Dropbox / Google Drive can revert versions

---

# Why Learn Git & GitHub

Git & GitHub are version control for **projects**.

You can:
* restore project states involving changes to multiple files.
* track *who* made *what* changes and *why*
* handle changes in any file format
* manage work from large distributed teams

---

# Example scenarios

* You change a histogram to a bar plot, and then you want to change it back.
* Your collaborator makes edits while traveling, and you need to combine their changes with changes you made in the meantime.
* You want to experiment with a different dataset / analysis / narrative without duplicating everything.

---

# Git and GitHub

--

## (not the same thing!)

---

# Git

* software and version control system
* notoriously unfriendly
  - unintuitive command names
  - obscure error messages

---

# GitHub

* a cloud platform that hosts Git repos
* unlimited *public* and *private* repos
* size limits:
  - 1 GB for each repo
  - 100 MB for individual files
* [GitHub Education](https://education.github.com/pack) has some benefits
  - one code for a free t-shirt from https://github.myshopify.com/ to be given away to a random attendee
  
---

class: inverse, center, middle

# Git enables time travel

---

---

---

---

class: inverse, center, middle

# Commits Are Project States

---

# Structure of a Commit


---

---

---

class: inverse, center, middle

# Branches Let You Experiment

---

# 


---

---

# The GitHub Flow System



---
class: inverse, center, middle

# GitHub as a Backup System

---

# 


---

---

---

class: inverse, center, middle

# GitHub as a Collaboration Platform

---

# 


---

---

---

---
# Thanks

* Check out the [Getting Started checklist](https://ha0ye.github.io/github-practices-BME6938/checklist.html) for actions to get started.
* Check out the [Resources](https://ha0ye.github.io/github-practices-BME6938/resources.html) page for tutorials and guides
* Contact me if you have questions or would like a (free) consultation on reproducibility / sharing of your data science project.
* https://guides.uflib.ufl.edu/reproducibility has more info and my contact info





